%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Luo Shengwen}} & Email : \href{mailto:sharwen568@gmail.com}{sharwen568@gmail.com}\\
  \href{https://github.com/fantasydreams/}{https://github.com/fantasydreams} & Mobile : +86-188-8328-7841 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Zhejiang University}{Hangzhou}
      {Master of computer Science and technology}{Sep. 2018 -- Apr. 2021}
    \resumeSubheading
      {Chongqing University of Posts and Telecommunications}{Chongqing}
      {Bachelor of computer Science and technology;  GPA: Top 10\%}{Sep. 2012 -- Jun. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {iSoftStone Information Technology (Group) Co., Ltd.}{Chengdu}
      {Senior Software Engineer}{Dec. 2016 - Apr. 2017}
      \resumeItemListStart
        \resumeItem{Target}
          {Rectified the TRAN module code in Huawei Wireless Transmission UNITRP platform to make it compatible with the x64 environment.}
        \resumeItem{Code adaptation}
         {Responsible for reviewing the TRAN module code and rectified the code that uses UINT32 to save pointers. The code modification rate is about 4\% and more than 8000 lines code were modified. }
         \resumeItem{Bugs fixed}
         {Two serious bugs were found and fixed when reviewing the code. , Email to all employees of Huawei TRAN department to read and circumvention.}
         \resumeItem{Log conversion module}
         {After communicating with the upper software department, an inter-department log interface conversion module that encapsulated the upper-level interface was designed to replace the old upper log interface in TRAN code with the new conversion interface.}
       
          
      \resumeItemListEnd

    \resumeSubheading
      {iSoftStone Information Technology (Group) Co., Ltd.}{Chengdu}
      {Senior Software Engineer}{Jul. 2016 - Nov. 2016}
      \resumeItemListStart
        \resumeItem{Target}
          {Transplanting the TRAN module in UNITRP from big-endian to little-endian x86, the forward system can forwarding basic data stream on x86, and test engineers can use the x86 environment instead of physical board to test.}
        \resumeItem{Code adaption}
          {Browse 20w+ lines of code, add conversion interface to the place where the data end-to-end conversion is involved, the code modification rate is about 10\%, and the personal workload is 1/3.}
        \resumeItem{Cross byte domain conversion module}
          {Design cross-byte domain conversion macro definition codes for different code modules and add the corresponding macros to the correct positions;.}
        \resumeItem{x86 transmission interface}
        {Independently encode the datagram transmission interface (Raw Socket, IPC) required for x86. After data flow was workable in the first code version, optimizing the code increase the transmission speed by 10 times. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Instant Messaging software}
      {An Instant Messaging software based on C\#.NET, Socket, SQLite and MySQL, design own protocol on application layer, we can use it send text, pictures, files, etc.}
    \resumeSubItem{PC cashier system}
      {A system for PC cash register based on vb.NET, SQLite and MySQL, including functions such as real-time reminders for orders.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C/C++, C\#.NET, SQL, Python}
   }
	\item{
	\textbf{Tools}{: visual studio, Git, MySQL, SQLite}	
   }
 \resumeSubHeadingListEnd
 
 \section{Awards}
 \resumeSubHeadingListStart
 \item{
 	\textbf{published a EI thesis  \textit{A Survey on Knowledge Graph Visualization} on CAD-Journal}
 	\hfill
 	\textbf{}{Oct. 2019}
   }
  \item{
 	\textbf{Outstanding graduate student, outstanding graduate cadre of Zhejiang University}
 	\hfill
 	\textbf{}{Sep. 2019}
   }
  \item{
  	\textbf{Second Prize of the Eighth Database Application Design Competition in Chongqing}
  	\hfill
  	\textbf{}{Jun. 2015}
   }
  \item{
  	\textbf{The first "Internet +" Chongqing Bronze Award in Chongqing}
  	\hfill
 	\textbf{}{Jun. 2015}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
